# Prediction and Prediction Errors

<br>

Let's return to looking at the relationship between `runs` and `at_bats`. We'll combine our graph before with our fitted regression line from the model superimposed on top. Recall the equation for the regression line is:

$$\textrm{Runs} = -2789 + 0.6305*\textrm{At-Bats}$$

```{r runsatbatsline, echo = TRUE, eval = FALSE}
ggplot(data = mlb11, aes(x = at_bats, y = runs)) +
    geom_point() +
    labs(title = "Relationship between Runs and At-Bats", x = "At-Bats", y = "Runs") +
    geom_smooth(method = "lm", se = FALSE)
```

Here, we are literally adding a layer on top of our plot. `geom_smooth` adds the regression line fitted by minimizing the errors sum of squares. It can also show us the standard error `se` associated with our line, but we won't show that for now, using the `se = FALSE` argument. (Although you can set `se = TRUE` if you're interested in looking at it. It essentially creates a continuous confidence interval for values around the regression line.)

The regression line can be used to predict $y$ at any value of $x$ within the range of observed $x$ values.. 

<br>

**Interpolation is when...**

```{r, echo = FALSE}
q_name <- sample(c(
   "Predictions for y are made from values of x outside the range of observed data.",
   answer = "Predictions for y are made from values of x within the range of observed data."
)
)
```

`r longmcq(q_name)`

<br>

**Extrapolation is when...**

```{r, echo = FALSE}
q_name <- sample(c(
   "Predictions for y are made from values of x within the range of observed data.",
   answer = "Predictions for y are made from values of x outside the range of observed data."
)
)
```

`r longmcq(q_name)`

Extrapolation is not usually recommended. Predictions made within the range of the data are more reliable, and are also used to compute the residuals.

<br>

Use the fitted model to answer the questions below.


## **Exercise 4**

To the nearest whole number, the New York Yankees had 867 runs and 5518 at-bats in the 2011 season. The residual for the New York Yankees is `r fitb(177)`

<br>

**Based on your previous answer, is the fitted value for the New York Yankees an overestimate or underestimate of their runs?**

```{r, echo = FALSE}
q_name <- sample(c(
    "An overestimate. The negative residual implies the observed value is larger than the fitted value i.e. the value given by the regression line has overestimated the actual value.",
    "An underestimate. The negative residual implies the fitted value is larger than the observed value i.e. the value given by the regression line has underestimated the actual value.",
    "An overestimate. The positive residual implies the fitted value is larger than the observed value i.e. the value given by the regression line has overestimated the actual value.",
    answer = "An underestimate. The positive residual implies the observed value is larger than the fitted value i.e. the value given by the regression line has underestimated the actual value."
)
)
```

`r longmcq(q_name)`

<br>

## **Exercise 5**

To the nearest whole number. the Chicago Cubs had 654 runs and 5549 at-bats in the 2011 season. The residual for the Chicago Cubs is (to 2 decimal places) `r fitb(-56)`

<br>

**Based on your previous answer, is the fitted value for the Chicago Cubs an overestimate or underestimate of their runs?**

```{r, echo = FALSE}
q_name <- sample(c(
    answer = "An overestimate. The negative residual implies the observed value is smaller than the fitted value i.e. the value given by the regression line has overestimated the actual value.",
    "An underestimate. The negative residual implies the observed value is smaller than the fitted value i.e. the value given by the regression line has underestimated the actual value.",
    "An overestimate. The positive residual implies the observed value is larger than the fitted value i.e. the value given by the regression line has overestimated the actual value.",
    "An underestimate. The negative residual implies the observed value is larger than the fitted value i.e. the value given by the regression line has underestimated the actual value."
)
)
```

`r longmcq(q_name)`

<br>
